Temporal ordering and registration of cross-sectional imaging data

### 2014-05-14 image_analysis_paper/si_information.tex
added more to si information

@@

\raisebox{3.7cm}{B}
\includegraphics[width=8.4cm]{data2_PCA_variance}
\caption{{\it A} Images shown in Figure~4 of the paper, now ordered by the first PCA projection coefficient. Note that the ordering is not consistent with the developmental dynamics. {\it B} The eigenvalue spectrum from PCA. Note that subsequent components have a nonnegligible contribution on the data.}
\end{figure}

@@

>>>>

\section{Image parameters}

For the images shown in Figure~3 of the paper, we only use the red and green channels (dpERK and Dl) to register the images.

For the images shown in Figure~4 of the paper, we use all three channels (dpERK, Twi, and nuclei) to register the images.
%
We blur the nuclei using a disc filter with radius $5$~pixels.
%
We also adjust the intensity of the nuclear signal such that 1\% of the pixels are saturated.

@@

\raisebox{3.7cm}{B}
\includegraphics[width=8.4cm]{data2_PCA_variance}
\caption{{\it (A)} Images shown in Figure~4 of the paper, now ordered by the first PCA projection coefficient. Note that the ordering is not consistent with the developmental dynamics. {\it (B)} The eigenvalue spectrum from PCA. Note that subsequent components have a nonnegligible contribution on the data.}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=8.4cm]{fig3}
\caption{{\it (A)} One-dimensional concentration profile on a ring (top), and the corresponding profile on a line (bottom). {\it (B)} Intensity corresponding to the profile in {\it A}. {\it (C)} An ensemble of concentration profiles, each of the form described in {\it A}. Each row in the array corresponds to a single profile. {\it (D)} The profiles in {\it C}, now registered using angular synchronization. {\it (E)} The profiles in {\it D}, now temporally ordered using diffusion maps. {\it (F)} The profiles in {\it C}, registered and temporally ordered in a single step using vector diffusion maps.}
\label{fig:1d_demo}
\end{figure}
